---
output: github_document
title: ChangChang manual
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    fig.path = "man/figures/README-",
    out.width = "100%"
)
```

# changchang

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![Bioc release status](http://www.bioconductor.org/shields/build/release/bioc/changchang.svg)](https://bioconductor.org/checkResults/release/bioc-LATEST/changchang)
[![Bioc devel status](http://www.bioconductor.org/shields/build/devel/bioc/changchang.svg)](https://bioconductor.org/checkResults/devel/bioc-LATEST/changchang)
[![Bioc downloads rank](https://bioconductor.org/shields/downloads/release/changchang.svg)](http://bioconductor.org/packages/stats/bioc/changchang/)
[![Bioc support](https://bioconductor.org/shields/posts/changchang.svg)](https://support.bioconductor.org/tag/changchang)
[![Bioc history](https://bioconductor.org/shields/years-in-bioc/changchang.svg)](https://bioconductor.org/packages/release/bioc/html/changchang.html#since)
[![Bioc last commit](https://bioconductor.org/shields/lastcommit/devel/bioc/changchang.svg)](http://bioconductor.org/checkResults/devel/bioc-LATEST/changchang/)
[![Bioc dependencies](https://bioconductor.org/shields/dependencies/release/changchang.svg)](https://bioconductor.org/packages/release/bioc/html/changchang.html#since)
<!-- badges: end -->

The goal of `changchang` is to ...

## Installation instructions

Get the latest stable `R` release from [CRAN](http://cran.r-project.org/). Then install `changchang` from [Bioconductor](http://bioconductor.org/) using the following code:

```{r 'install', eval = FALSE}
if (!requireNamespace("BiocManager", quietly = TRUE)) {
    install.packages("BiocManager")
}

BiocManager::install("changchang")
```

## Input data

### `tantan`

To load output of `tantan` the simplest at the moment is to convert its output
to BED format and use the `loadTantan()` function.  Here is an exmaple on how
to produce the BED file.

```
tantan -w 10 -f4 example.fasta | tee example.tantan.txt | awk 'OFS="\t" {print $1, $2, $3, $6, $5, "."}'  > example.tantan.bed
```

### Other tandem repeat finder softwares

Not supported yet.  Patches welcome!

## Example

This is a basic example which shows you how to solve a common problem:

```{r example, eval = requireNamespace('changchang')}
library("changchang") |> suppressPackageStartupMessages()
loadTantan(system.file('extdata/example.bed.xz', package="changchang"))
telomeres(exampleTantan, narrow="ends")
```

## Citation

Below is the citation output from using `citation('changchang')` in R. Please
run this yourself to check for any updates on how to cite __changchang__.

```{r 'citation', eval = requireNamespace('changchang')}
print(citation('changchang'), bibtex = TRUE)
```

Please note that the `changchang` was only made possible thanks to many other R and bioinformatics software authors, which are cited either in the vignettes and/or the paper(s) describing this package.

## Code of Conduct

Please note that the `changchang` project is released with a [Contributor Code of Conduct](http://bioconductor.org/about/code-of-conduct/). By contributing to this project, you agree to abide by its terms.

## Development tools

* Continuous code testing is possible thanks to [GitHub actions](https://www.tidyverse.org/blog/2020/04/usethis-1-6-0/)  through `r BiocStyle::CRANpkg('usethis')`, `r BiocStyle::CRANpkg('remotes')`, and `r BiocStyle::CRANpkg('rcmdcheck')` customized to use [Bioconductor's docker containers](https://www.bioconductor.org/help/docker/) and `r BiocStyle::Biocpkg('BiocCheck')`.
* Code coverage assessment is possible thanks to [codecov](https://codecov.io/gh) and `r BiocStyle::CRANpkg('covr')`.
* The code is styled automatically thanks to `r BiocStyle::CRANpkg('styler')`.
* The documentation is formatted thanks to `r BiocStyle::CRANpkg('devtools')` and `r BiocStyle::CRANpkg('roxygen2')`.

For more details, check the `dev` directory.

This package was developed using `r BiocStyle::Biocpkg('biocthis')`.


